---
title: "anesrake weights"
author: "Lewis White"
date: "2023-11-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## load libraries
```{r}
library(tidyverse)
library(survey)
library(anesrake)
```

## Set working directory 
```{r}
setwd("/Users/lewiswhite/CHAP_columbia/CHAP_survey_weights")
```

## Loading in the data
```{r}
#includes the weights from Linnea and Flavio's V4 weights 
GL_EA_weights <- read_csv("weight_2010_full_results.csv")

#responses to the survey
demographics <- read_csv("Demographics dataset.csv")

#cooking survey
primary_secondary_cooking <- read_csv("Primary and secondary cooking practices dataset.csv")
```

## Recalculating Linnea and Flavio's weights in R
```{r}
LW_EA_weights <- GL_EA_weights %>%
  select(!prob_1:weight_2010) %>% #remove weighting variables 
  mutate(ea_select_prob = eas_selected/eas_2010, #Prob select the cluster (EA)
         hh_select_within_ea_prob = 20/ea_hhs_2010) %>% #Prob select HH within each EA
  mutate(hh_select_prob = ea_select_prob * hh_select_within_ea_prob) %>% #prob select HH 
  mutate(weight = 1/hh_select_prob) #obtain weight
```

## Joining the demographic and cooking data 
```{r}
#join the weights to the demographic data
survey_with_weights <- left_join(demographics, LW_EA_weights, by = c("eacode", "region")) %>%
  filter(!is.na(weight))

#add the cooking data
full_survey <- left_join(survey_with_weights, primary_secondary_cooking, by = "hh_id") %>%
  
  #add LPG main cookstove column
  mutate(LPG_main = ifelse(primary_cookstove == "Gas:(LPG)/cooking gas stove", "Yes", "No")) %>%
  
  #add charcoal/wood main cookstove column
  mutate(CW_main = ifelse(primary_cookstove == "3-stone stove/open fire" | primary_cookstove == "Charcoal stove", "Yes", "No")) %>%
  
  #change NA values in charcoal/lpg main to "No". These respondents skipped over this question bc they don't cook
  mutate(LPG_main = coalesce(LPG_main, "No"),
         CW_main = coalesce(CW_main, "No"))
```

## Collapsing region and primary cooking type 
```{r}
#collapse some of the regions and fuel types so there are enough in each group ----
full_survey_collapsed <- full_survey %>%
  
  #collapse region
  mutate(collapsed_region = case_when(
  region == "Western" | region == "Western North" ~ "west_west_north",
  region %in% c("Upper East", "Upper West", "North East", 
                "Northern", "Savannah", "Oti") ~ "northern_regions",
  region %in% c("Bono", "Bono East", "Ahafo") ~ "mid_west_regions",
  TRUE ~ region)) %>%
  
  #collapse fuel type
  mutate(collapsed_fuel = case_when(
    primary_cookstove == "Gas:(LPG)/cooking gas stove" ~ "LPG",
    primary_cookstove == "Charcoal stove" ~ "charcoal",
    primary_cookstove == "3-stone stove/open fire" ~ "wood",
    is.na(primary_cookstove) ~ "none_other",
    TRUE ~ "none_other"
  )) %>%

  #FOR ANESRAKE, IT IS ESSENTIAL THAT THE COLUMNS ARE OF CLASS FACTOR
  mutate(urban_rural_str = as.factor(urban_rural_str), 
         collapsed_fuel = as.factor(collapsed_fuel),
         region = as.factor(region)) %>%
  
  as.data.frame() #FOR ANESRAKE, IT IS ESSENTIAL THAT THE DATA IS IN THIS FORMAT, NOT TIBBLE DF
```


# Rake 5: Anesrake with national urban/rural split, national fuel use, and 2021 population in each region 

## population proportions 

```{r}
# Set target variables 

#FUEL
collapsed_fuel <- c('none_other', 'wood', 'LPG', 'charcoal')
collapsed_fuel_freq = c(732934, 2594937, 3086324, 1942771)
collapsed_fuel_prop <- collapsed_fuel_freq/sum(collapsed_fuel_freq)

collapsed_fuel_df <- data_frame(collapsed_fuel, collapsed_fuel_prop) %>%
  mutate(collapsed_fuel = as.factor(collapsed_fuel))

#LOCALITY
urban_rural_str <- c('urban', 'rural')
urban_rural_str_freq <- c(5090702, 3254711)
urban_rural_str_prop <- urban_rural_str_freq/sum(urban_rural_str_freq)

urban_rural_str_df <- data_frame(urban_rural_str, urban_rural_str_prop) %>%
  mutate(urban_rural_str = as.factor(urban_rural_str))

#REGION
region <- c("Western", "Central", "Greater Accra", "Volta", "Eastern", "Ashanti", "Western North", "Ahafo", "Bono", "Bono East", "Oti", "Northern", "Savannah", "North East", "Upper East", "Upper West")
region_freq <- c(621349, 838493, 1702160, 491373, 881328, 1523101, 240086, 152801, 317994, 288725, 174031, 437934, 133114, 108088, 264404, 190193)
region_prop <- region_freq/sum(region_freq)

region_df <- data_frame(region, region_prop) %>%
  mutate(region = as.factor(region))


#set up target list of proportions for each variable of interest
target <- list(
  
  collapsed_fuel = weights::wpct(collapsed_fuel_df$collapsed_fuel, collapsed_fuel_df$collapsed_fuel_prop),
  
  urban_rural_str = weights::wpct(urban_rural_str_df$urban_rural_str, urban_rural_str_df$urban_rural_str_prop),
  
  region = weights::wpct(region_df$region, region_df$region_prop)
)

#make sure names of the variables in the list match the survey data
names(target) <- c("collapsed_fuel", "urban_rural_str", "region")
```

# check out survey proportions for the same variables
```{r}
weights::wpct(full_survey_collapsed$collapsed_fuel)

weights::wpct(full_survey_collapsed$urban_rural_str)

weights::wpct(full_survey_collapsed$region)
```

# complete the raking
```{r}
CHAP_raking <- anesrake(target,            # target list identified above
                    full_survey_collapsed,              # survey dataset 
                    full_survey_collapsed$hh_id,    # unique identifier for each respondent
                    cap = 5,  # Maximum value for any given weight
                    weightvec = full_survey_collapsed$weight, #initial weights
                    choosemethod = "total",       # How are parameters compared for selection (other options include 'average' and 'max')
                    type = "pctlim",              # What targets should be used to weight 
                    pctlim = 0.05                 # Threshold for deviation
                    )

#raking achieved only partial convergence -- no improvement was apparent after 22 iterations
```

### obtain raking results
```{r}
raking_summary <- summary(CHAP_raking)
```

### check out specific for each target variable
```{r}
raking_summary$collapsed_fuel

raking_summary$urban_rural_str

raking_summary$region
```

### check out design effect
```{r}
raking_summary$general.design.effect #weighting caused a 94.9% increase in the variance
```

## obtain vector of new weights and add them to the full_survey_collapsed df
```{r}
caseweights <- data.frame(cases=CHAP_raking$caseid, weights=CHAP_raking$weightvec)

full_survey_collapsed$ames_weights <- CHAP_raking$weightvec
```

### testing out the results
```{r}
#pct urban/rural 
wpct(full_survey_collapsed$urban_rural_str)

wpct(full_survey_collapsed$urban_rural_str, full_survey_collapsed$ames_weights)


#main fuel
wpct(full_survey_collapsed$collapsed_fuel)

wpct(full_survey_collapsed$collapsed_fuel, full_survey_collapsed$ames_weights)


#main fuel urban
urban <- full_survey_collapsed %>%
  filter(urban_rural_str == "urban") 

wpct(urban$collapsed_fuel, urban$ames_weights)

#main fuel rural 
rural <- full_survey_collapsed %>%
  filter(urban_rural_str == "rural") 

wpct(rural$collapsed_fuel, rural$ames_weights)

#main fuel greater accra
accra <- full_survey_collapsed %>%
  filter(region == "Greater Accra") 

wpct(accra$collapsed_fuel, accra$ames_weights)

#main fuel ashanti
ashanti <- full_survey_collapsed %>%
  filter(region == "Ashanti") 

wpct(ashanti$collapsed_fuel, ashanti$ames_weights)


#hh num ---- 
hh_nums <- wpct(full_survey_collapsed$total_hh_num, full_survey_collapsed$ames_weights) * 8345414 #calculating the mean hh num feels more complicated than it should

hh_num_seq <- seq(1, 20)
hh_num_seq <- hh_num_seq[hh_num_seq != 18]

result <- numeric(length(hh_num_seq))

for (i in 1:length(hh_num_seq)) {
  result[i] <- hh_num_seq[i] * hh_nums[i]
}

sum(result) / 8345414



#hh num urban ---- 
hh_nums_urban <- wpct(urban$total_hh_num, urban$ames_weights) * 5090702 

hh_num_seq_urban <- seq(1, 20)
hh_num_seq_urban <- hh_num_seq[hh_num_seq != 18 & hh_num_seq != 19]

result <- numeric(length(hh_num_seq_urban))

for (i in 1:length(hh_num_seq_urban)) {
  result[i] <- hh_num_seq_urban[i] * hh_nums_urban[i]
}

sum(result) / 5090702


#hh num rural ---- 
hh_nums_rural <- wpct(rural$total_hh_num, rural$ames_weights) * 3254711 

hh_num_seq_rural <- seq(1, 20)
hh_num_seq_rural <- hh_num_seq[hh_num_seq != 18 & hh_num_seq != 19]

result <- numeric(length(hh_num_seq_rural))

for (i in 1:length(hh_num_seq_rural)) {
  result[i] <- hh_num_seq_rural[i] * hh_nums_rural[i]
}

sum(result) / 3254711
```

## observe weighting to see which combinations lead to strongest weights
```{r}
full_survey_collapsed %>% 
  select(urban_rural_str, collapsed_fuel, region, ames_weights) %>% 
  unique() %>% 
  group_by(urban_rural_str, collapsed_fuel, region) %>%
  summarise(mean_ames_weight = mean(ames_weights)) %>%
  arrange(-mean_ames_weight)

full_survey_collapsed %>%
  group_by(urban_rural_str) %>%
  summarise(n = n(),
            sum_weights.= sum(ames_weights))

#can multiply all weights by 8345414/7389 (1129.438) to scale to national weighting 

full_survey_collapsed$scaled_ames_weights <- full_survey_collapsed$ames_weights * 1129.438


full_survey_collapsed %>%
  pivot_longer(cols = c(weight, scaled_ames_weights), names_to = "Variable", values_to = "Value") %>%
  ggplot(aes(x = Value, fill = Variable)) +
  geom_histogram(bins = 30, position = "identity", alpha = 0.6) +
  labs(title = "Histogram of Weights: Rake 5",
       x = "Survey Weight",
       y = "Frequency",
       fill = "Weight Origin") +
  theme_bw() +
  scale_fill_manual(values = c("scaled_ames_weights" = "#a8605d", 
                               "weight" = "#7fabc7"),
                    labels = c("scaled_ames_weights" = "Amesrake", 
                               "weight" = "Original Weights")) 
```


# Rake 6: Anesrake with national urban/rural split and number of households in each region 2021

## population proportions 

```{r}
# Set target variables 

#LOCALITY
urban_rural_str <- c('urban', 'rural')
urban_rural_str_freq <- c(5090702, 3254711)
urban_rural_str_prop <- urban_rural_str_freq/sum(urban_rural_str_freq)

urban_rural_str_df <- data_frame(urban_rural_str, urban_rural_str_prop) %>%
  mutate(urban_rural_str = as.factor(urban_rural_str))

#REGION
region <- c("Western", "Central", "Greater Accra", "Volta", "Eastern", "Ashanti", "Western North", "Ahafo", "Bono", "Bono East", "Oti", "Northern", "Savannah", "North East", "Upper East", "Upper West")
region_freq <- c(621349, 838493, 1702160, 491373, 881328, 1523101, 240086, 152801, 317994, 288725, 174031, 437934, 133114, 108088, 264404, 190193)
region_prop <- region_freq/sum(region_freq)

region_df <- data_frame(region, region_prop) %>%
  mutate(region = as.factor(region))


#set up target list of proportions for each variable of interest
target <- list(
  
  urban_rural_str = weights::wpct(urban_rural_str_df$urban_rural_str, urban_rural_str_df$urban_rural_str_prop),
  
  region = weights::wpct(region_df$region, region_df$region_prop)
)

#make sure names of the variables in the list match the survey data
names(target) <- c("urban_rural_str", "region")
```

## check out survey proportions for the same variables
```{r}
weights::wpct(full_survey_collapsed$urban_rural_str)

weights::wpct(full_survey_collapsed$region)
```

## complete the raking
```{r}
CHAP_raking <- anesrake(target,            # target list identified above
                    full_survey_collapsed,              # survey dataset 
                    full_survey_collapsed$hh_id,    # unique identifier for each respondent
                    cap = 5,  # Maximum value for any given weight
                    weightvec = full_survey_collapsed$weight, #initial weights
                    choosemethod = "total",       # How are parameters compared for selection (other options include 'average' and 'max')
                    type = "pctlim",              # What targets should be used to weight 
                    pctlim = 0.05                 # Threshold for deviation
                    )

#raking converged in 20 iterations
```

### obtain raking results
```{r}
raking_summary <- summary(CHAP_raking)
```

### check out specific for each target variable
```{r}
raking_summary$urban_rural_str

raking_summary$region
```

### check out design effect
```{r}
raking_summary$general.design.effect #weighting caused a 64.9% increase in the variance
```

## obtain vector of new weights and add them to the full_survey_collapsed df
```{r}
caseweights <- data.frame(cases=CHAP_raking$caseid, weights=CHAP_raking$weightvec)

full_survey_collapsed$ames_weights <- CHAP_raking$weightvec
```

### testing out the results
```{r}
#pct urban/rural 
wpct(full_survey_collapsed$urban_rural_str)

wpct(full_survey_collapsed$urban_rural_str, full_survey_collapsed$ames_weights)


#main fuel
wpct(full_survey_collapsed$collapsed_fuel)

wpct(full_survey_collapsed$collapsed_fuel, full_survey_collapsed$ames_weights)


#main fuel urban
urban <- full_survey_collapsed %>%
  filter(urban_rural_str == "urban") 

wpct(urban$collapsed_fuel, urban$ames_weights)

#main fuel rural 
rural <- full_survey_collapsed %>%
  filter(urban_rural_str == "rural") 

wpct(rural$collapsed_fuel, rural$ames_weights)

#main fuel greater accra
accra <- full_survey_collapsed %>%
  filter(region == "Greater Accra") 

wpct(accra$collapsed_fuel, accra$ames_weights)

#main fuel ashanti
ashanti <- full_survey_collapsed %>%
  filter(region == "Ashanti") 

wpct(ashanti$collapsed_fuel, ashanti$ames_weights)


#hh num ---- 
hh_nums <- wpct(full_survey_collapsed$total_hh_num, full_survey_collapsed$ames_weights) * 8345414 #calculating the mean hh num feels more complicated than it should

hh_num_seq <- seq(1, 20)
hh_num_seq <- hh_num_seq[hh_num_seq != 18]

result <- numeric(length(hh_num_seq))

for (i in 1:length(hh_num_seq)) {
  result[i] <- hh_num_seq[i] * hh_nums[i]
}

sum(result) / 8345414



#hh num urban ---- 
hh_nums_urban <- wpct(urban$total_hh_num, urban$ames_weights) * 5090702 

hh_num_seq_urban <- seq(1, 20)
hh_num_seq_urban <- hh_num_seq[hh_num_seq != 18 & hh_num_seq != 19]

result <- numeric(length(hh_num_seq_urban))

for (i in 1:length(hh_num_seq_urban)) {
  result[i] <- hh_num_seq_urban[i] * hh_nums_urban[i]
}

sum(result) / 5090702


#hh num rural ---- 
hh_nums_rural <- wpct(rural$total_hh_num, rural$ames_weights) * 3254711 

hh_num_seq_rural <- seq(1, 20)
hh_num_seq_rural <- hh_num_seq[hh_num_seq != 18 & hh_num_seq != 19]

result <- numeric(length(hh_num_seq_rural))

for (i in 1:length(hh_num_seq_rural)) {
  result[i] <- hh_num_seq_rural[i] * hh_nums_rural[i]
}

sum(result) / 3254711
```

## observe weighting to see which combinations lead to strongest weights
```{r}
full_survey_collapsed %>% 
  select(urban_rural_str, collapsed_fuel, region, ames_weights) %>% 
  unique() %>% 
  group_by(urban_rural_str, collapsed_fuel, region) %>%
  summarise(mean_ames_weight = mean(ames_weights)) %>%
  arrange(-mean_ames_weight)

full_survey_collapsed %>%
  group_by(urban_rural_str) %>%
  summarise(n = n(),
            sum_weights.= sum(ames_weights))

#can multiply all weights by 8345414/7389 (1129.438) to scale to national weighting 

full_survey_collapsed$scaled_ames_weights <- full_survey_collapsed$ames_weights * 1129.438


full_survey_collapsed %>%
  pivot_longer(cols = c(weight, scaled_ames_weights), names_to = "Variable", values_to = "Value") %>%
  ggplot(aes(x = Value, fill = Variable)) +
  geom_histogram(bins = 30, position = "identity", alpha = 0.6) +
  labs(title = "Histogram of Weights: Rake 6",
       x = "Survey Weight",
       y = "Frequency",
       fill = "Weight Origin") +
  theme_bw() +
  scale_fill_manual(values = c("scaled_ames_weights" = "#a8605d", 
                               "weight" = "#7fabc7"),
                    labels = c("scaled_ames_weights" = "Amesrake", 
                               "weight" = "Original Weights")) 
```