---
title: "Raking Sensitivity Analysis"
author: "Lewis White"
date: "2023-12-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load libraries
```{r, message=FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(survey)
library(readxl)
```

## Set Paths
```{r, message=FALSE, warning = FALSE}
if (Sys.getenv('USER') == "lewiswhite") {
    
  # set working directory
  setwd("/Users/lewiswhite/CHAP_columbia/CHAP_survey_weights")
  
  #includes the weights from Linnea and Flavio's V4 weights 
  GL_EA_weights <- read_csv("data/weight_2010_full_results.csv")
  
  #responses to the survey
  demographics <- read_csv("data/Demographics dataset.csv")
  
  #cooking survey
  primary_secondary_cooking <- read_csv("data/Primary and secondary cooking practices dataset.csv")
  
  #house structure
  house_structure <- read_csv("data/House structure (non randomized).csv")
  
  house_structure_random <- read_csv("data/House structure (randomized).csv")
  
  #lighting 
  lighting <- read_csv("data/Lighting.csv")
  
  #GSS-2021
  gss <- read_excel("data/gss_2021.xlsx")
     
}

if (Sys.getenv('USER') == "linneagraham") {

  ROOT <- ("/Volumes/GoogleDrive-100807402805951836278/.shortcut-targets-by-id/1B0iSt7ZGnvhcH8p5MtZccbjg10Pho9qT/ColumbiaWorldProjectsGhana/03_Phase_1/01_Assessment_Household_Needs")

  GL_EA_weights <- read_csv(file.path(ROOT, "Survey Weights/output/weight_2010_full_results.csv"))

  demographics <- read_csv(file.path(ROOT, "Public Use Dataset/Modules/Demographics dataset.csv"))
  primary_secondary_cooking <- read_csv(file.path(ROOT,"Public Use Dataset/Modules/Primary and secondary cooking practices dataset.csv"))
  house_structure <- read_csv(file.path(ROOT, "Public Use Dataset/Modules/House structure (non randomized).csv"))
  
  house_structure_random <- read_csv(file.path(ROOT, "Public Use Dataset/Modules/House structure (randomized).csv"))
  
  lighting <- read_csv(file.path(ROOT, "Public Use Dataset/Modules/Lighting.csv"))

  gss <- read_excel(file.path(ROOT, "Survey Weights/input/gss_2021.xlsx"))
}

```

## Recalculating Linnea and Flavio's weights in R
```{r, message=FALSE, warning = FALSE}
LW_EA_weights <- GL_EA_weights %>%
  select(!prob_1:weight_2010) %>% #remove weighting variables 
  mutate(ea_select_prob = eas_selected/eas_2010, #Prob select the cluster (EA)
         hh_select_within_ea_prob = 20/ea_hhs_2010) %>% #Prob select HH within each EA
  mutate(hh_select_prob = ea_select_prob * hh_select_within_ea_prob) %>% #prob select HH 
  mutate(weight = 1/hh_select_prob) #obtain weight
```

## Joining the demographic and cooking data 
```{r, message=FALSE, warning = FALSE}
#join the weights to the demographic data
survey_with_weights <- left_join(demographics, LW_EA_weights, by = c("eacode", "region")) %>%
  filter(!is.na(weight))

#add the cooking data
full_survey <- left_join(survey_with_weights, primary_secondary_cooking, by = "hh_id") %>%
  
  #add LPG main cookstove column
  mutate(LPG_main = ifelse(primary_cookstove == "Gas:(LPG)/cooking gas stove", "Yes", "No")) %>%
  
  #add charcoal/wood main cookstove column
  mutate(CW_main = ifelse(primary_cookstove == "3-stone stove/open fire" | primary_cookstove == "Charcoal stove", "Yes", "No")) %>%
  
  #change NA values in charcoal/lpg main to "No". These respondents skipped over this question bc they don't cook
  mutate(LPG_main = coalesce(LPG_main, "No"),
         CW_main = coalesce(CW_main, "No")) %>%
  
  #add in house structure data
  left_join(house_structure) %>%
  
  left_join(house_structure_random) %>%
  
  #add lighting data
  left_join(lighting)
```


# RAKE 4a

## Adding collapsed region and collapsed primary cooking type 
```{r, message=FALSE, warning = FALSE}
#collapse some of the regions and fuel types so there are enough in each group ----
full_survey_collapsed <- full_survey %>%
  
  #collapse region
  mutate(collapsed_region = case_when(
  region %in% c("Ashanti", "Eastern") ~ "middle",
  region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Bono", "Bono East", "Ahafo") ~ "northern",
  region %in% c("Greater Accra", "Volta") ~ "southeast",
  region %in% c("Central", "Western", "Western North") ~ "southwest",
  TRUE ~ region)) %>%
  
  #collapse fuel type
  mutate(collapsed_fuel = case_when(
    primary_cookstove == "Gas:(LPG)/cooking gas stove" ~ "LPG",
    primary_cookstove == "Charcoal stove" ~ "charcoal",
    primary_cookstove == "3-stone stove/open fire" ~ "wood",
    is.na(primary_cookstove) ~ "none_other",
    TRUE ~ "none_other"
  )) %>%
  
  #add house room indicators
  mutate(rooms_two_plus = case_when(
    house_rooms > 1 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  
  #add sleeping rooms indicator 
  mutate(sleeping_rooms_two_plus = case_when(
    house_rooms_sleep > 1 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  
  mutate(separate_cooking = case_when(
    house_rooms_cooking > 0 ~ "Yes",
    TRUE ~ "No"
  ))
```

### check out survey distribution of collapsed fuel and collapsed region to check for small groups
```{r, message=FALSE, warning = FALSE}
full_survey_collapsed %>% group_by(collapsed_fuel, collapsed_region) %>% count()
```

## Setting up the population tables

## National population totals 
```{r, message=FALSE, warning = FALSE}
#total household pop
hh_pop_tot <- subset(gss, region == "Total")$hh_pop

### urban/rural total
pop.urban_rural_str <-
  data.frame(
    urban_rural_str = c("urban", "rural"),
    Freq = c(
      subset(gss, region == "Total")$hh_pop_urban,
      subset(gss, region == "Total")$hh_pop_rural
    )
  )

### primary fuel categories 
frac_lpg <- subset(gss, region == "Total")$fuel_lpg / subset(gss, region == "Total")$hh_pop_fuel
frac_char <- subset(gss, region == "Total")$fuel_char / subset(gss, region == "Total")$hh_pop_fuel
frac_wood <- subset(gss, region == "Total")$fuel_wood / subset(gss, region == "Total")$hh_pop_fuel
  
pop.primary_fuel <-
  data.frame(
    collapsed_fuel = c("none_other", "wood", "LPG", "charcoal"),
    Freq = c(
      round((1 - (frac_lpg + frac_wood + frac_char)) * hh_pop_tot, 0),
      round(frac_wood * hh_pop_tot, 0),
      round(frac_lpg * hh_pop_tot, 0),
      round(frac_char * hh_pop_tot, 0)
    )
  )
```

## Regional population totals 
```{r, message=FALSE, warning = FALSE}
### regional 2021 HH populations 
gss_regional <- filter(gss, region != "Total") 

pop.region_hh <- data.frame(
  region = gss_regional$region,
  Freq = gss_regional$hh_pop
)
```

### regional main fuel
```{r, message=FALSE, warning = FALSE}
#specify known main fuel population values for each of the regions 
pop.region_main_fuel <- gss_regional %>% 
  mutate(none_other = fuel_none + fuel_other) %>%
  rename(LPG = fuel_lpg, 
         wood = fuel_wood, 
         charcoal = fuel_char) %>%
  select(region, none_other, wood, LPG, charcoal) %>%
  
  #apply scaling factor so population matches GSS total value
  mutate(none_other = round(none_other * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0),
         LPG = round(LPG * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel,0),
         wood = round(wood * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0),
         charcoal = round(charcoal * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0))

northern <- pop.region_main_fuel %>%
  filter(region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Bono", "Bono East", "Ahafo")) %>%
  summarise(
    region = "northern",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )


middle <- pop.region_main_fuel %>%
  filter(region %in% c("Ashanti", "Eastern")) %>%
  summarise(
    region = "middle",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )

southeast <- pop.region_main_fuel %>%
  filter(region %in% c("Greater Accra", "Volta")) %>%
  summarise(
    region = "southeast",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )

southwest <- pop.region_main_fuel %>%
  filter(region %in% c("Central", "Western", "Western North")) %>%
  summarise(
    region = "southwest",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )

collapsed_region_primary_fuel <- bind_rows(northern, middle, southeast, southwest)


#Combine primary fuel with each row specifying which is applicable 
pop_region_primary_fuel_long <- collapsed_region_primary_fuel %>%
  pivot_longer(cols = c(none_other, wood, LPG, charcoal), names_to = "collapsed_fuel", values_to = "Count") #names need to match what is in the survey!!

# reformat this data so each row is a household (necessary for creating pop.table below)
pop_region_primary_fuel_long <- pop_region_primary_fuel_long %>%
  uncount(Count) %>%
  rename(collapsed_region = region)

#create table of LPG main stove by collapsed regions
pop.table_primary_fuel <- xtabs(~collapsed_region+collapsed_fuel, pop_region_primary_fuel_long)
```

### regional urban/rural 
```{r, message=FALSE, warning = FALSE}
#regional 2021 HH populations 
pop.region_urban_rural_hh <- gss_regional %>%
  select(region, hh_pop_rural, hh_pop_urban) %>%
  rename(rural = hh_pop_rural, 
         urban = hh_pop_urban)


northern <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Bono", "Bono East", "Ahafo")) %>%
  summarise(
    region = "northern",
    urban = sum(urban),
    rural = sum(rural)
  )


middle <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Ashanti", "Eastern")) %>%
  summarise(
    region = "middle",
    urban = sum(urban),
    rural = sum(rural)
  )

southeast <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Greater Accra", "Volta")) %>%
  summarise(
    region = "southeast",
    urban = sum(urban),
    rural = sum(rural)
  )

southwest <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Central", "Western", "Western North")) %>%
  summarise(
    region = "southwest",
    urban = sum(urban),
    rural = sum(rural)
  )

collapsed_region_urban_rural_hh <- bind_rows(northern, middle, southeast, southwest)


#Combine LPG yes/no columns with each row specifying which is applicable 
pop_region_urban_rural_long <- collapsed_region_urban_rural_hh %>%
  pivot_longer(cols = c(rural, urban), names_to = "urban_rural_str", values_to = "Count") #names need to match what is in the survey!!

# reformat this data so each row is a household (necessary for creating pop.table below)
pop_region_urban_rural_long <- pop_region_urban_rural_long %>%
  uncount(Count) %>%
  rename(collapsed_region = region)

#create table of LPG main stove by collapsed regions
pop.table_urban_rural <- xtabs(~collapsed_region+urban_rural_str, pop_region_urban_rural_long)
```


## Setting up the initial survey design
```{r, message=FALSE, warning = FALSE}
#specify the initial survey design again
survey_design <- svydesign(id=~eacode, #specify clusters
                           weights= ~weight, #specify the survey weights
                           strata= ~region, #specify the region strata
                           data=full_survey_collapsed)

#fpc was removed because we are sampling less than 5% of the EAs
```



## Starting the raking
```{r, message=FALSE, warning = FALSE}
raked_surv <- rake(survey_design, 
                   
                   list(~urban_rural_str+collapsed_region,
                        ~collapsed_region+collapsed_fuel,
                        ~region), 
                   
                   list(pop.table_urban_rural, 
                        pop.table_primary_fuel,
                        pop.region_hh), 
                   
                   control = list(maxit = 15, epsilon = 1))

upper_weight <- mean(weights(raked_surv, type = "sampling")) * 5

trimmed_raked_surv <- trimWeights(raked_surv, lower=0.1, upper=upper_weight,
                                   strict = TRUE)
```

## National Population Results from Rake 4a

```{r, message=FALSE, warning = FALSE}
#total population
survey::svytotal(c(rep(1, nrow(full_survey))), trimmed_raked_surv)

#urban/rural totals
svytotal(~urban_rural_str, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~urban_rural_str, design = trimmed_raked_surv, na.rm = TRUE))

#region hh populations 
svytotal(~region, design = trimmed_raked_surv, na.rm = TRUE)

#mean hh members
svymean(~total_hh_num, design = trimmed_raked_surv, na.rm = TRUE)
confint(svymean(~total_hh_num, design = trimmed_raked_surv, na.rm = TRUE))

#LPG main stove
svytotal(~collapsed_fuel, design = trimmed_raked_surv)
confint(svytotal(~collapsed_fuel, design = trimmed_raked_surv))


#URBAN
#urban subset 
urban_sub <- subset(trimmed_raked_surv, urban_rural == 1)

#urban hh size
svymean(~total_hh_num, design = urban_sub, na.rm = TRUE)
confint(svymean(~total_hh_num, design = urban_sub, na.rm = TRUE))

#urban LPG primary stove 
svytotal(~collapsed_fuel, design = urban_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = urban_sub, na.rm = TRUE))


#RURAL
#rural subset
rural_sub <- subset(trimmed_raked_surv, urban_rural == 2)

# rural hh size 
svymean(~total_hh_num, design = rural_sub, na.rm = TRUE)
confint(svymean(~total_hh_num, design = rural_sub, na.rm = TRUE))

# rural LPG primary stove
svytotal(~collapsed_fuel, design = rural_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = rural_sub, na.rm = TRUE))


#Greater Accra LPG
accra_sub <- subset(trimmed_raked_surv, region == "Greater Accra")
svytotal(~collapsed_fuel, design = accra_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = accra_sub, na.rm = TRUE))

#Ashanti LPG
ashanti_sub <- subset(trimmed_raked_surv, region == "Ashanti")
svytotal(~collapsed_fuel, design = ashanti_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = ashanti_sub, na.rm = TRUE))


#check out hh structures
svytotal(~hh_water_source, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~hh_water_source, design = trimmed_raked_surv, na.rm = TRUE))

svymean(~house_rooms, design = trimmed_raked_surv, na.rm = TRUE)

#check out house rooms
svytotal(~rooms_two_plus, design = trimmed_raked_surv)
confint(svytotal(~rooms_two_plus, design = trimmed_raked_surv))

svytotal(~sleeping_rooms_two_plus, design = trimmed_raked_surv)
confint(svytotal(~sleeping_rooms_two_plus, design = trimmed_raked_surv))

svytotal(~separate_cooking, design = trimmed_raked_surv)
confint(svytotal(~separate_cooking, design = trimmed_raked_surv))

#check out lighting 
svytotal(~light_source_main, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~light_source_main, design = trimmed_raked_surv, na.rm = TRUE))
```

## writing a loop to find main fuel counts 

```{r, message=FALSE, warning = FALSE}
#obtain a list of the regions
regions <- gss_regional$region

#loop through each of the regions in the list 
for (i in seq_along(regions)){
  
  #subset the raked survey to the region
  region_subset = subset(trimmed_raked_surv, region == regions[i])
  
  #create list of regions populations
  regions_pop <- pop.region_hh[[2]]
  
  #obtain population for specific region in the loop
  region_pop = regions_pop[i]
  
  #get the fuel information for the region
  region_fuel  <- as.data.frame(svytotal(~collapsed_fuel, 
                                         design = region_subset, 
                                         na.rm = TRUE))
  
  #obtain just the LPG total for the region 
  region_lpg <- region_fuel[2,1]
  
  #calculate the percent LPG for the region
  region_pct_lpg <- round((region_lpg/region_pop)*100,1)
  
  #print the result for each
  print(region_pct_lpg)
}
```


## Examine new weights from Rake 4a

```{r, message=FALSE, warning = FALSE}
#Identify new weights from raking process
raked_weights <- weights(trimmed_raked_surv, type = "sampling")

#add new weights to full dataframe
survey_all_weights <- bind_cols(survey_with_weights, raked_weights) %>%
  rename("rake_weight" = "...58") %>%
  mutate(weight_diff = rake_weight - weight,
         weight_ratio = rake_weight / weight)

#graphing the original weights with the comparison
survey_all_weights %>%
  pivot_longer(cols = c(weight, rake_weight), names_to = "Variable", values_to = "Value") %>%
  ggplot(aes(x = Value, fill = Variable)) +
  geom_histogram(bins = 30, position = "identity", alpha = 0.6) +
  labs(title = "Histogram of Weights: Rake 4a",
       x = "Survey Weight",
       y = "Frequency",
       fill = "Weight Origin") +
  theme_bw() +
  scale_fill_manual(values = c("rake_weight" = "#a8605d", 
                               "weight" = "#7fabc7"),
                    labels = c("rake_weight" = "Raked Weight", 
                               "weight" = "Original Weights")) 

#create df with hh_id and weights to be exported
survey_all_weights_4a <- survey_all_weights %>% select(hh_id, rake_weight) %>%
  mutate(rake_method = "4a")

# Write the tibble to a CSV file
write_csv(survey_all_weights_4a, "rake_4a_weights.csv")
```

## Chi Square tests
```{r}
rake_lpg <- svytable(~collapsed_fuel+region, raked_surv) %>%
  as.data.frame() %>% 
  filter(collapsed_fuel == "LPG") %>%
  select(region, Freq) %>%
  rename(rake_lpg = Freq)

gss_lpg <- gss %>% select(region, fuel_lpg) %>%
  filter(region != "Total") %>%
  arrange(region) %>%
  rename(gss_lpg = fuel_lpg)

expected_props = gss_lpg$gss_lpg / sum(gss_lpg$gss_lpg)
observed_counts = rake_lpg$rake_lpg

# Perform chi-squared test
chisq.test(observed_counts, p = expected_props) # p < 2.2e-16


rake_urban <- svytable(~urban_rural_str+region, raked_surv) %>%
  as.data.frame() %>%
  filter(urban_rural_str == "urban") %>%
  select(region, Freq)

gss_urban <- gss %>% select(region, hh_pop_urban) %>%
  filter(region != "Total") %>%
  arrange(region)

expected_props = gss_urban$hh_pop_urban / sum(gss_urban$hh_pop_urban)
observed_counts = rake_urban$Freq

# Perform chi-squared test
chisq.test(observed_counts, p = expected_props) # p < 2.2e-16

```


# RAKE 4b

## Adding collapsed region and collapsd primary cooking type 
```{r, message=FALSE, warning = FALSE}
#collapse some of the regions and fuel types so there are enough in each group ----
full_survey_collapsed <- full_survey %>%
  
  #collapse region
  mutate(collapsed_region = case_when(
  region %in% c("Ashanti", "Eastern") ~ "middle",
  region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo") ~ "northern",
  region %in% c("Greater Accra", "Volta", "Central", "Western") ~ "coastal",
  TRUE ~ region)) %>%
  
  #collapse fuel type
  mutate(collapsed_fuel = case_when(
    primary_cookstove == "Gas:(LPG)/cooking gas stove" ~ "LPG",
    primary_cookstove == "Charcoal stove" ~ "charcoal",
    primary_cookstove == "3-stone stove/open fire" ~ "wood",
    is.na(primary_cookstove) ~ "none_other",
    TRUE ~ "none_other"
  )) %>%
  
  #add house room indicators
  mutate(rooms_two_plus = case_when(
    house_rooms > 1 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  
  #add sleeping rooms indicator 
  mutate(sleeping_rooms_two_plus = case_when(
    house_rooms_sleep > 1 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  
  mutate(separate_cooking = case_when(
    house_rooms_cooking > 0 ~ "Yes",
    TRUE ~ "No"
  ))
```

## checking out counts for collapsed region and fuel for survey
```{r, message=FALSE, warning = FALSE}
full_survey_collapsed %>% group_by(collapsed_region, collapsed_fuel) %>% count()
```


## Setting up the initial survey design 
```{r, message=FALSE, warning = FALSE}
# Survey design using survey package
survey_design <- svydesign(id=~eacode, #specify clusters 
                           weights= ~weight, #specify the survey weights
                           strata= ~region, #specify the region strata
                           data=full_survey_collapsed)
```


##  POPULATION VALUES

## National population totals 

```{r, message=FALSE, warning = FALSE}
#total household pop
hh_pop_tot <- subset(gss, region == "Total")$hh_pop

### urban/rural total
pop.urban_rural_str <-
  data.frame(
    urban_rural_str = c("urban", "rural"),
    Freq = c(
      subset(gss, region == "Total")$hh_pop_urban,
      subset(gss, region == "Total")$hh_pop_rural
    )
  )

### primary fuel categories 
frac_lpg <- subset(gss, region == "Total")$fuel_lpg / subset(gss, region == "Total")$hh_pop_fuel
frac_char <- subset(gss, region == "Total")$fuel_char / subset(gss, region == "Total")$hh_pop_fuel
frac_wood <- subset(gss, region == "Total")$fuel_wood / subset(gss, region == "Total")$hh_pop_fuel
  
pop.primary_fuel <-
  data.frame(
    collapsed_fuel = c("none_other", "wood", "LPG", "charcoal"),
    Freq = c(
      round((1 - (frac_lpg + frac_wood + frac_char)) * hh_pop_tot, 0),
      round(frac_wood * hh_pop_tot, 0),
      round(frac_lpg * hh_pop_tot, 0),
      round(frac_char * hh_pop_tot, 0)
    )
  )
```

## Regional population totals 

```{r, message=FALSE, warning = FALSE}
### regional 2021 HH populations 
gss_regional <- filter(gss, region != "Total") 

pop.region_hh <- data.frame(
  region = gss_regional$region,
  Freq = gss_regional$hh_pop
)
```


### regional main fuel
```{r, message=FALSE, warning = FALSE}
#specify known main fuel population values for each of the regions 
pop.region_main_fuel <- gss_regional %>% 
  mutate(none_other = fuel_none + fuel_other) %>%
  rename(LPG = fuel_lpg, 
         wood = fuel_wood, 
         charcoal = fuel_char) %>%
  select(region, none_other, wood, LPG, charcoal) %>%
  
  #apply scaling factor so population matches GSS total value
  mutate(none_other = round(none_other * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0),
         LPG = round(LPG * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel,0),
         wood = round(wood * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0),
         charcoal = round(charcoal * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0))


northern <- pop.region_main_fuel %>%
  filter(region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo")) %>%
  summarise(
    region = "northern",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )


middle <- pop.region_main_fuel %>%
  filter(region %in% c("Ashanti", "Eastern")) %>%
  summarise(
    region = "middle",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )

coastal <- pop.region_main_fuel %>%
  filter(region %in% c("Greater Accra", "Volta", "Central", "Western")) %>%
  summarise(
    region = "coastal",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )


collapsed_region_primary_fuel <- bind_rows(northern, middle, coastal)


#Combine primary fuel with each row specifying which is applicable 
pop_region_primary_fuel_long <- collapsed_region_primary_fuel %>%
  pivot_longer(cols = c(none_other, wood, LPG, charcoal), names_to = "collapsed_fuel", values_to = "Count") #names need to match what is in the survey!!

# reformat this data so each row is a household (necessary for creating pop.table below)
pop_region_primary_fuel_long <- pop_region_primary_fuel_long %>%
  uncount(Count) %>%
  rename(collapsed_region = region)

#create table of LPG main stove by collapsed regions
pop.table_primary_fuel <- xtabs(~collapsed_region+collapsed_fuel, pop_region_primary_fuel_long)
```

### regional urban/rural 
```{r, message=FALSE, warning = FALSE}
#regional 2021 HH populations 
pop.region_urban_rural_hh <- gss_regional %>%
  select(region, hh_pop_rural, hh_pop_urban) %>%
  rename(rural = hh_pop_rural, 
         urban = hh_pop_urban)


# get population urban/rural split for each region of the collapsed regions ----
northern <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo")) %>%
  summarise(
    region = "northern",
    urban = sum(urban),
    rural = sum(rural)
  )

middle <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Ashanti", "Eastern")) %>%
  summarise(
    region = "middle",
    urban = sum(urban),
    rural = sum(rural)
  )

coastal <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Greater Accra", "Volta", "Central", "Western")) %>%
  summarise(
    region = "coastal",
    urban = sum(urban),
    rural = sum(rural)
  )


collapsed_region_urban_rural_hh <- bind_rows(northern, middle, coastal)

#Combine LPG yes/no columns with each row specifying which is applicable 
pop_region_urban_rural_long <- collapsed_region_urban_rural_hh %>%
  pivot_longer(cols = c(rural, urban), names_to = "urban_rural_str", values_to = "Count") #names need to match what is in the survey!!

# reformat this data so each row is a household (necessary for creating pop.table below)
pop_region_urban_rural_long <- pop_region_urban_rural_long %>%
  uncount(Count) %>%
  rename(collapsed_region = region)

#create table of LPG main stove by collapsed regions
pop.table_urban_rural <- xtabs(~collapsed_region+urban_rural_str, pop_region_urban_rural_long)
```


## Starting the raking
```{r, message=FALSE, warning = FALSE}
raked_surv <- rake(survey_design, 
                   
                   list(~urban_rural_str+collapsed_region,
                        ~collapsed_region+collapsed_fuel,
                        ~region), 
                   list(pop.table_urban_rural, 
                        pop.table_primary_fuel,
                        pop.region_hh), 
                   
                   control = list(maxit = 15, epsilon = 1))

upper_weight <- mean(weights(raked_surv, type = "sampling")) * 5

trimmed_raked_surv <- trimWeights(raked_surv, lower=0.1, upper=upper_weight,
                                   strict = TRUE)
```
## National Population Results from Rake 4b

```{r, message=FALSE, warning = FALSE}
#total population
survey::svytotal(c(rep(1, nrow(full_survey))), trimmed_raked_surv)

#urban/rural totals
svytotal(~urban_rural_str, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~urban_rural_str, design = trimmed_raked_surv, na.rm = TRUE))

#region hh populations 
svytotal(~region, design = trimmed_raked_surv, na.rm = TRUE)

#mean hh members
svymean(~total_hh_num, design = trimmed_raked_surv, na.rm = TRUE)
confint(svymean(~total_hh_num, design = trimmed_raked_surv, na.rm = TRUE))

#LPG main stove
svytotal(~collapsed_fuel, design = trimmed_raked_surv)
confint(svytotal(~collapsed_fuel, design = trimmed_raked_surv))


#URBAN
#urban subset 
urban_sub <- subset(trimmed_raked_surv, urban_rural == 1)

#urban hh size
svymean(~total_hh_num, design = urban_sub, na.rm = TRUE)
confint(svymean(~total_hh_num, design = urban_sub, na.rm = TRUE))

#urban LPG primary stove 
svytotal(~collapsed_fuel, design = urban_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = urban_sub, na.rm = TRUE))


#RURAL
#rural subset
rural_sub <- subset(trimmed_raked_surv, urban_rural == 2)

# rural hh size 
svymean(~total_hh_num, design = rural_sub, na.rm = TRUE)
confint(svymean(~total_hh_num, design = rural_sub, na.rm = TRUE))

# rural LPG primary stove
svytotal(~collapsed_fuel, design = rural_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = rural_sub, na.rm = TRUE))


#Greater Accra LPG
accra_sub <- subset(trimmed_raked_surv, region == "Greater Accra")
svytotal(~collapsed_fuel, design = accra_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = accra_sub, na.rm = TRUE))

#Ashanti LPG
ashanti_sub <- subset(trimmed_raked_surv, region == "Ashanti")
svytotal(~collapsed_fuel, design = ashanti_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = ashanti_sub, na.rm = TRUE))


#check out hh structures
svytotal(~hh_water_source, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~hh_water_source, design = trimmed_raked_surv, na.rm = TRUE))

svymean(~house_rooms, design = trimmed_raked_surv, na.rm = TRUE)

#check out house rooms
svytotal(~rooms_two_plus, design = trimmed_raked_surv)
confint(svytotal(~rooms_two_plus, design = trimmed_raked_surv))

svytotal(~sleeping_rooms_two_plus, design = trimmed_raked_surv)
confint(svytotal(~sleeping_rooms_two_plus, design = trimmed_raked_surv))

svytotal(~separate_cooking, design = trimmed_raked_surv)
confint(svytotal(~separate_cooking, design = trimmed_raked_surv))

#check out lighting 
svytotal(~light_source_main, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~light_source_main, design = trimmed_raked_surv, na.rm = TRUE))
```

## writing a loop to find main fuel counts 

```{r, message=FALSE, warning = FALSE}
#obtain a list of the regions
regions <- gss_regional$region

#loop through each of the regions in the list 
for (i in seq_along(regions)){
  
  #subset the raked survey to the region
  region_subset = subset(trimmed_raked_surv, region == regions[i])
  
  #create list of regions populations
  regions_pop <- pop.region_hh[[2]]
  
  #obtain population for specific region in the loop
  region_pop = regions_pop[i]
  
  #get the fuel information for the region
  region_fuel  <- as.data.frame(svytotal(~collapsed_fuel, 
                                         design = region_subset, 
                                         na.rm = TRUE))
  
  #obtain just the LPG total for the region 
  region_lpg <- region_fuel[2,1]
  
  #calculate the percent LPG for the region
  region_pct_lpg <- round((region_lpg/region_pop)*100,1)
  
  #print the result for each
  print(region_pct_lpg)
}
```

## Examine new weights from Rake 4b

```{r, message=FALSE, warning = FALSE}
#Identify new weights from raking process
raked_weights <- weights(trimmed_raked_surv, type = "sampling")

#add new weights to full dataframe
survey_all_weights <- bind_cols(survey_with_weights, raked_weights) %>%
  rename("rake_weight" = "...58") %>%
  mutate(weight_diff = rake_weight - weight,
         weight_ratio = rake_weight / weight)

#graphing the original weights with the comparison
survey_all_weights %>%
  pivot_longer(cols = c(weight, rake_weight), names_to = "Variable", values_to = "Value") %>%
  ggplot(aes(x = Value, fill = Variable)) +
  geom_histogram(bins = 30, position = "identity", alpha = 0.6) +
  labs(title = "Histogram of Weights: Rake 4b",
       x = "Survey Weight",
       y = "Frequency",
       fill = "Weight Origin") +
  theme_bw() +
  scale_fill_manual(values = c("rake_weight" = "#a8605d", 
                               "weight" = "#7fabc7"),
                    labels = c("rake_weight" = "Raked Weight", 
                               "weight" = "Original Weights")) 

#create df with hh_id and weights to be exported
survey_all_weights_4b <- survey_all_weights %>% select(hh_id, rake_weight) %>%
  mutate(rake_method = "4b")

# Write the tibble to a CSV file
write_csv(survey_all_weights_4b, "rake_4b_weights.csv")
```




# RAKE 4c

## Adding collapsed region and collapsd primary cooking type 
```{r, message=FALSE, warning = FALSE}
#collapse some of the regions and fuel types so there are enough in each group ----
full_survey_collapsed <- full_survey %>%
  
  #collapse region
  mutate(collapsed_region = case_when(
  region %in% c("Ashanti", "Eastern", "Volta") ~ "middle",
  region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo") ~ "northern",
  region %in% c("Greater Accra", "Central", "Western") ~ "coastal",
  TRUE ~ region)) %>%
  
  #collapse fuel type
  mutate(collapsed_fuel = case_when(
    primary_cookstove == "Gas:(LPG)/cooking gas stove" ~ "LPG",
    primary_cookstove == "Charcoal stove" ~ "charcoal",
    primary_cookstove == "3-stone stove/open fire" ~ "wood",
    is.na(primary_cookstove) ~ "none_other",
    TRUE ~ "none_other"
  )) %>%
  
  #add house room indicators
  mutate(rooms_two_plus = case_when(
    house_rooms > 1 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  
  #add sleeping rooms indicator 
  mutate(sleeping_rooms_two_plus = case_when(
    house_rooms_sleep > 1 ~ "Yes",
    TRUE ~ "No"
  )) %>%
  
  mutate(separate_cooking = case_when(
    house_rooms_cooking > 0 ~ "Yes",
    TRUE ~ "No"
  ))
```


## checking out counts for collapsed region and fuel for survey
```{r, message=FALSE, warning = FALSE}
full_survey_collapsed %>% group_by(collapsed_region, collapsed_fuel) %>% count()
```


## Setting up the initial survey design 
```{r, message=FALSE, warning = FALSE}
# Survey design using survey package
survey_design <- svydesign(id=~eacode, #specify clusters 
                           weights= ~weight, #specify the survey weights
                           strata= ~region, #specify the region strata
                           data=full_survey_collapsed)
```


##  POPULATION VALUES

## National population totals 
```{r, message=FALSE, warning = FALSE}
#total household pop
hh_pop_tot <- subset(gss, region == "Total")$hh_pop

### urban/rural total
pop.urban_rural_str <-
  data.frame(
    urban_rural_str = c("urban", "rural"),
    Freq = c(
      subset(gss, region == "Total")$hh_pop_urban,
      subset(gss, region == "Total")$hh_pop_rural
    )
  )

### primary fuel categories 
frac_lpg <- subset(gss, region == "Total")$fuel_lpg / subset(gss, region == "Total")$hh_pop_fuel
frac_char <- subset(gss, region == "Total")$fuel_char / subset(gss, region == "Total")$hh_pop_fuel
frac_wood <- subset(gss, region == "Total")$fuel_wood / subset(gss, region == "Total")$hh_pop_fuel
  
pop.primary_fuel <-
  data.frame(
    collapsed_fuel = c("none_other", "wood", "LPG", "charcoal"),
    Freq = c(
      round((1 - (frac_lpg + frac_wood + frac_char)) * hh_pop_tot, 0),
      round(frac_wood * hh_pop_tot, 0),
      round(frac_lpg * hh_pop_tot, 0),
      round(frac_char * hh_pop_tot, 0)
    )
  )
```

## Regional population totals 

```{r, message=FALSE, warning = FALSE}
### regional 2021 HH populations 
gss_regional <- filter(gss, region != "Total") 

pop.region_hh <- data.frame(
  region = gss_regional$region,
  Freq = gss_regional$hh_pop
)
```


### regional main fuel
```{r, message=FALSE, warning = FALSE}
#specify known main fuel population values for each of the regions 
pop.region_main_fuel <- gss_regional %>% 
  mutate(none_other = fuel_none + fuel_other) %>%
  rename(LPG = fuel_lpg, 
         wood = fuel_wood, 
         charcoal = fuel_char) %>%
  select(region, none_other, wood, LPG, charcoal) %>%
  
  #apply scaling factor so population matches GSS total value
  mutate(none_other = round(none_other * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0),
         LPG = round(LPG * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel,0),
         wood = round(wood * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0),
         charcoal = round(charcoal * subset(gss, region == "Total")$hh_pop/subset(gss, region == "Total")$hh_pop_fuel, 0))


northern <- pop.region_main_fuel %>%
  filter(region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo")) %>%
  summarise(
    region = "northern",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )


middle <- pop.region_main_fuel %>%
  filter(region %in% c("Ashanti", "Eastern", "Volta")) %>%
  summarise(
    region = "middle",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )

coastal <- pop.region_main_fuel %>%
  filter(region %in% c("Greater Accra", "Central", "Western")) %>%
  summarise(
    region = "coastal",
    none_other = sum(none_other),
    wood = sum(wood),
    LPG = sum(LPG),
    charcoal = sum(charcoal)
  )


collapsed_region_primary_fuel <- bind_rows(northern, middle, coastal)


#Combine primary fuel with each row specifying which is applicable 
pop_region_primary_fuel_long <- collapsed_region_primary_fuel %>%
  pivot_longer(cols = c(none_other, wood, LPG, charcoal), names_to = "collapsed_fuel", values_to = "Count") #names need to match what is in the survey!!

# reformat this data so each row is a household (necessary for creating pop.table below)
pop_region_primary_fuel_long <- pop_region_primary_fuel_long %>%
  uncount(Count) %>%
  rename(collapsed_region = region)

#create table of LPG main stove by collapsed regions
pop.table_primary_fuel <- xtabs(~collapsed_region+collapsed_fuel, pop_region_primary_fuel_long)
```

### regional urban/rural 
```{r, message=FALSE, warning = FALSE}
#regional 2021 HH populations 
pop.region_urban_rural_hh <- gss_regional %>%
  select(region, hh_pop_rural, hh_pop_urban) %>%
  rename(rural = hh_pop_rural, 
         urban = hh_pop_urban)

# get population urban/rural split for each region of the collapsed regions ----
northern <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Upper East", "Upper West", "North East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo")) %>%
  summarise(
    region = "northern",
    urban = sum(urban),
    rural = sum(rural)
  )

middle <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Ashanti", "Eastern", "Volta")) %>%
  summarise(
    region = "middle",
    urban = sum(urban),
    rural = sum(rural)
  )

coastal <- pop.region_urban_rural_hh %>%
  filter(region %in% c("Greater Accra", "Central", "Western")) %>%
  summarise(
    region = "coastal",
    urban = sum(urban),
    rural = sum(rural)
  )


collapsed_region_urban_rural_hh <- bind_rows(northern, middle, coastal)

#Combine LPG yes/no columns with each row specifying which is applicable 
pop_region_urban_rural_long <- collapsed_region_urban_rural_hh %>%
  pivot_longer(cols = c(rural, urban), names_to = "urban_rural_str", values_to = "Count") #names need to match what is in the survey!!

# reformat this data so each row is a household (necessary for creating pop.table below)
pop_region_urban_rural_long <- pop_region_urban_rural_long %>%
  uncount(Count) %>%
  rename(collapsed_region = region)

#create table of LPG main stove by collapsed regions
pop.table_urban_rural <- xtabs(~collapsed_region+urban_rural_str, pop_region_urban_rural_long)
```


## Starting the raking
```{r, message=FALSE, warning = FALSE}
raked_surv <- rake(survey_design, 
                   
                   list(~urban_rural_str+collapsed_region,
                        ~collapsed_region+collapsed_fuel,
                        ~region), 
                   list(pop.table_urban_rural, 
                        pop.table_primary_fuel,
                        pop.region_hh), 
                   
                   control = list(maxit = 15, epsilon = 1))

upper_weight <- mean(weights(raked_surv, type = "sampling")) * 5

trimmed_raked_surv <- trimWeights(raked_surv, lower=0.1, upper=upper_weight,
                                   strict = TRUE)
```

## National Population Results from Rake 4c
```{r, message=FALSE, warning = FALSE}
#total population
survey::svytotal(c(rep(1, nrow(full_survey))), trimmed_raked_surv)


#urban/rural totals
svytotal(~urban_rural_str, design = trimmed_raked_surv, na.rm = TRUE)

confint(svytotal(~urban_rural_str, design = trimmed_raked_surv, na.rm = TRUE))

#region hh populations 
svytotal(~region, design = trimmed_raked_surv, na.rm = TRUE)

#mean hh members
svymean(~total_hh_num, design = trimmed_raked_surv, na.rm = TRUE)

confint(svymean(~total_hh_num, design = trimmed_raked_surv, na.rm = TRUE))

#LPG main stove
svytotal(~collapsed_fuel, design = trimmed_raked_surv)

confint(svytotal(~collapsed_fuel, design = trimmed_raked_surv))

#URBAN
#urban subset 
urban_sub <- subset(trimmed_raked_surv, urban_rural == 1)

#urban hh size
svymean(~total_hh_num, design = urban_sub, na.rm = TRUE)

confint(svymean(~total_hh_num, design = urban_sub, na.rm = TRUE))

#urban LPG primary stove 
svytotal(~collapsed_fuel, design = urban_sub, na.rm = TRUE)

confint(svytotal(~collapsed_fuel, design = urban_sub, na.rm = TRUE))


#RURAL
#rural subset
rural_sub <- subset(trimmed_raked_surv, urban_rural == 2)

# rural hh size 
svymean(~total_hh_num, design = rural_sub, na.rm = TRUE)

confint(svymean(~total_hh_num, design = rural_sub, na.rm = TRUE))

# rural LPG primary stove
svytotal(~collapsed_fuel, design = rural_sub, na.rm = TRUE)

confint(svytotal(~collapsed_fuel, design = rural_sub, na.rm = TRUE))


#Greater Accra LPG
accra_sub <- subset(trimmed_raked_surv, region == "Greater Accra")
svytotal(~collapsed_fuel, design = accra_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = accra_sub, na.rm = TRUE))

#Ashanti LPG
ashanti_sub <- subset(trimmed_raked_surv, region == "Ashanti")
svytotal(~collapsed_fuel, design = ashanti_sub, na.rm = TRUE)
confint(svytotal(~collapsed_fuel, design = ashanti_sub, na.rm = TRUE))


#check out hh structures
svytotal(~hh_water_source, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~hh_water_source, design = trimmed_raked_surv, na.rm = TRUE))

svymean(~house_rooms, design = trimmed_raked_surv, na.rm = TRUE)

#check out house rooms
svytotal(~rooms_two_plus, design = trimmed_raked_surv)
confint(svytotal(~rooms_two_plus, design = trimmed_raked_surv))

svytotal(~sleeping_rooms_two_plus, design = trimmed_raked_surv)
confint(svytotal(~sleeping_rooms_two_plus, design = trimmed_raked_surv))

svytotal(~separate_cooking, design = trimmed_raked_surv)
confint(svytotal(~separate_cooking, design = trimmed_raked_surv))

#check out lighting 
svytotal(~light_source_main, design = trimmed_raked_surv, na.rm = TRUE)
confint(svytotal(~light_source_main, design = trimmed_raked_surv, na.rm = TRUE))

```

## writing a loop to find main fuel counts 

```{r, message=FALSE, warning = FALSE}
#obtain a list of the regions
regions <- gss_regional$region

#loop through each of the regions in the list 
for (i in seq_along(regions)){
  
  #subset the raked survey to the region
  region_subset = subset(trimmed_raked_surv, region == regions[i])
  
  #create list of regions populations
  regions_pop <- pop.region_hh[[2]]
  
  #obtain population for specific region in the loop
  region_pop = regions_pop[i]
  
  #get the fuel information for the region
  region_fuel  <- as.data.frame(svytotal(~collapsed_fuel, 
                                         design = region_subset, 
                                         na.rm = TRUE))
  
  #obtain just the LPG total for the region 
  region_lpg <- region_fuel[2,1]
  
  #calculate the percent LPG for the region
  region_pct_lpg <- round((region_lpg/region_pop)*100,1)
  
  #print the result for each
  print(region_pct_lpg)
}
```

## Examine new weights from Rake 4c

```{r, message=FALSE, warning = FALSE}
#Identify new weights from raking process
raked_weights <- weights(trimmed_raked_surv, type = "sampling")

#add new weights to full dataframe
survey_all_weights <- bind_cols(survey_with_weights, raked_weights) %>%
  rename("rake_weight" = "...58") %>%
  mutate(weight_diff = rake_weight - weight,
         weight_ratio = rake_weight / weight)

#graphing the original weights with the comparison
survey_all_weights %>%
  pivot_longer(cols = c(weight, rake_weight), names_to = "Variable", values_to = "Value") %>%
  ggplot(aes(x = Value, fill = Variable)) +
  geom_histogram(bins = 30, position = "identity", alpha = 0.6) +
  labs(title = "Histogram of Weights: Rake 4c",
       x = "Survey Weight",
       y = "Frequency",
       fill = "Weight Origin") +
  theme_bw() +
  scale_fill_manual(values = c("rake_weight" = "#a8605d", 
                               "weight" = "#7fabc7"),
                    labels = c("rake_weight" = "Raked Weight", 
                               "weight" = "Original Weights")) 

#create df with hh_id and weights to be exported
survey_all_weights_4c <- survey_all_weights %>% select(hh_id, rake_weight) %>%
  mutate(rake_method = "4c")

# Write the tibble to a CSV file
write_csv(survey_all_weights_4c, "rake_4c_weights.csv")
```



# Visualizing the region divides

```{r, message=FALSE, warning = FALSE}
library(sf)
library(here)

country <- st_read(here("gha_admbnda_gss_20210308_SHP", "gha_admbnda_adm0_gss_20210308.shp"))

regions <- st_read(here("gha_admbnda_gss_20210308_SHP", "gha_admbnda_adm1_gss_20210308.shp")) %>%
  rename(region = ADM1_EN)


ggplot() +
  geom_sf(data = regions, aes(fill = region)) +
  theme_minimal() +
  labs(fill = "Region",
       title = "Regions of Ghana")+
  theme(plot.title = element_text(size = 20)) +
  theme(
    axis.text = element_blank(),  # Remove axis text
    axis.title = element_blank(),  # Remove axis titles
    panel.grid = element_blank()
  )



rake1_regions <- regions %>%
  mutate(collapsed_region = case_when(
  region %in% c("Ashanti", "Eastern") ~ "middle",
  region %in% c("Upper East", "Upper West", "Northern East", "Northern", "Savannah", "Oti", "Bono", "Bono East", "Ahafo") ~ "northern",
  region %in% c("Greater Accra", "Volta") ~ "southeast",
  region %in% c("Central", "Western", "Western North") ~ "southwest",
  TRUE ~ region)) %>%
  mutate(collapsed_region = factor(collapsed_region, levels = c("northern", "middle", "southeast", "southwest")))

# Define custom colors for each region
custom_colors <- c("middle" = "#2b8f6d", 
                   "northern" = "#58b368", 
                   "southeast" = "#bcba50", 
                   "southwest" = "#EFEEB4"
                   )

ggplot() +
  geom_sf(data = rake1_regions, aes(fill = collapsed_region)) +
  scale_fill_manual(values = custom_colors) +
  theme_minimal() +
  labs(fill = "Region",
       title = "Rake 4a Collapsed Regions") +
  theme(plot.title = element_text(size = 20)) +
  theme(
    axis.text = element_blank(),  # Remove axis text
    axis.title = element_blank(),  # Remove axis titles
    panel.grid = element_blank()
  )



rake2_regions <- regions %>%
  mutate(collapsed_region = case_when(
  region %in% c("Ashanti", "Eastern") ~ "middle",
  region %in% c("Upper East", "Upper West", "Northern East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo") ~ "northern",
  region %in% c("Greater Accra", "Volta", "Central", "Western") ~ "coastal",
  TRUE ~ region)) %>%
  mutate(collapsed_region = factor(collapsed_region, levels = c("northern", "middle", "coastal")))

# Define custom colors for each region
custom_colors <- c("middle" = "#2b8f6d", 
                   "northern" = "#58b368", 
                   "coastal" = "#EFEEB4"
                   )

ggplot() +
  geom_sf(data = rake2_regions, aes(fill = collapsed_region)) +
  scale_fill_manual(values = custom_colors) +
  theme_minimal() +
  labs(fill = "Region",
       title = "Rake 4b Collapsed Regions") +
  theme(plot.title = element_text(size = 20)) +
  theme(
    axis.text = element_blank(),  # Remove axis text
    axis.title = element_blank(),  # Remove axis titles
    panel.grid = element_blank()
  )




rake3_regions <- regions %>%
  mutate(collapsed_region = case_when(
  region %in% c("Ashanti", "Eastern", "Volta") ~ "middle",
  region %in% c("Upper East", "Upper West", "Northern East", "Northern", "Savannah", "Oti", "Western North", "Bono", "Bono East", "Ahafo") ~ "northern",
  region %in% c("Greater Accra", "Central", "Western") ~ "coastal",
  TRUE ~ region)) %>%
  mutate(collapsed_region = factor(collapsed_region, levels = c("northern", "middle", "coastal")))

# Define custom colors for each region
custom_colors <- c("middle" = "#2b8f6d", 
                   "northern" = "#58b368", 
                   "coastal" = "#EFEEB4"
                   )

ggplot() +
  geom_sf(data = rake3_regions, aes(fill = collapsed_region)) +
  scale_fill_manual(values = custom_colors) +
  theme_minimal() +
  labs(fill = "Region",
       title = "Rake 4c Collapsed Regions") +
  theme(plot.title = element_text(size = 20)) +
  theme(
    axis.text = element_blank(),  # Remove axis text
    axis.title = element_blank(),  # Remove axis titles
    panel.grid = element_blank()
  )
```


```{r}
sensitivity_weights <- bind_rows(survey_all_weights_4a, survey_all_weights_4b, survey_all_weights_4c) %>%
  pivot_wider(names_from = rake_method, values_from = rake_weight, names_prefix = "rake_method_")

write_csv(sensitivity_weights, "sensitivity_weights")

```



